Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-01-30 alloscore_manuscript/alloscore-application-shorter.tex

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Jan 29 16:46:53 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{Comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

>>>>

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Jan 29 16:46:53 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  percap & 865 &  & 1029 & 366 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{Comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}
